---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(phosphoricons)
cat(as.character(ph("lightning", type = "thin", height = "256px", width = "256px")), file = "man/figures/lightning-thin.svg")
cat(as.character(ph("lightning", type = "light", height = "256px", width = "256px")), file = "man/figures/lightning-light.svg")
cat(as.character(ph("lightning", type = "regular", height = "256px", width = "256px")), file = "man/figures/lightning-regular.svg")
cat(as.character(ph("lightning", type = "bold", height = "256px", width = "256px")), file = "man/figures/lightning-bold.svg")
cat(as.character(ph("lightning", type = "fill", height = "256px", width = "256px")), file = "man/figures/lightning-fill.svg")
cat(as.character(ph("lightning", type = "bold", fill = "gold", height = "256px", width = "256px")), file = "man/figures/lightning-bold-gold.svg")
```

# phosphoricons

<!-- badges: start -->
<!-- badges: end -->

Use [Phosphor Icons](https://github.com/phosphor-icons/phosphor-icons) in shiny applications or rmarkdown documents. Visit [phosphoricons.com](https://phosphoricons.com/) for a list of all available icons.

## Installation

You can install {phosphoricons} from GitHub with:

```r
remotes::install_github("dreamRs/phosphoricons")
```


## Example

Create an icon with `ph()` function:

```{r basic, eval=FALSE}
library(phosphoricons)
ph("lightning")
```
![](man/figures/lightning-light.svg){height=32}


There's 5 types of icon:

```{r type-thin, eval=FALSE}
ph("lightning", type = "thin")
```
![](man/figures/lightning-thin.svg){height=32}
```{r type-light, eval=FALSE}
ph("lightning", type = "light")
```
![](man/figures/lightning-light.svg){height=32}
```{r type-regular, eval=FALSE}
ph("lightning", type = "regular")
```
![](man/figures/lightning-regular.svg){height=32}
```{r type-bold, eval=FALSE}
ph("lightning", type = "bold")
```
![](man/figures/lightning-bold.svg){height=32}
```{r type-fill, eval=FALSE}
ph("lightning", type = "fill")
```
![](man/figures/lightning-fill.svg){height=32}

Colorize icon usin fill argument:

```{r color-icon, eval=FALSE}
ph("lightning", type = "bold", fill = "gold")
```
![](man/figures/lightning-bold-gold.svg){height=32}


